%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Relational algebra & relational calculus for Sailer-Reserve-Boat
% schema in the DBMS book.
% Author: Shuo Yang
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[10pt]{article}
\usepackage{amsmath,amssymb,epsfig,graphics,hyperref,amsthm,mathtools}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

\hypersetup{colorlinks=true}

\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.575in}
\setlength{\textheight}{9.25in}
\setlength{\oddsidemargin}{-.25in}
\setlength{\evensidemargin}{-.25in}

\reversemarginpar
\setlength{\marginparsep}{-15mm}

\newcommand{\rmv}[1]{}
\newcommand{\bemph}[1]{{\bfseries\itshape#1}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\imply}{\to}
\newcommand{\bic}{\leftrightarrow}

\def\Author{Shuo Yang}

\begin{document}

\noindent

\begin{center}
  Sailer-Boat-Reserve Queries\\
  \Author\\
\end{center}

% A horizontal split line
\hrule\smallskip

\vspace{1em}
\underline{Schema}:
\vspace{1em}

Sailor(\underline{\emph{sid}: integer}, \emph{sname}: string,
\emph{rating}: integer, \emph{age}: real)

Boat(\underline{\emph{bid}: integer}, \emph{bname}: string,
\emph{color}: string)

Reserve(\underline{\emph{sid}: integer, \emph{bid}: integer,
  \emph{day}: date}) \\

\underline{Tables}:
\vspace{1em}

Sailor:
\vspace{0.5em}

\begin{tabular} {| l | l | l | l |}
  \hline
  sid & sname & rating & age\\\hline

  22 & Dustin & 7 & 45.0\\
  29 & Brutus & 1 & 33.0\\
  31 & Lubber & 8 & 55.5\\
  32 & Andy & 8 & 25.5\\
  58 & Rusty & 10 & 35.0\\
  64 & Horatio & 7 & 35.0\\
  71 & Zorba & 10 & 16.0\\
  74 & Horatio & 9 & 35.0\\
  85 & Art & 3 & 25.5\\
  95 & Bob & 3 & 63.5\\\hline
\end{tabular}

\vspace{1em}
Boat:
\vspace{0.5em}

\begin{tabular} {| l | l | l |}
  \hline
  bid & bname & color \\\hline

  101 & Interlake & blue\\
  102 & Interlake & red\\
  103 & Clipper & green\\
  104 & Marine & red\\\hline
\end{tabular}

\vspace{1em}
Reserve:
\vspace{0.5em}

\begin{tabular} {| l | l | l |}
  \hline
  sid & bid & day \\\hline

  22 & 101 & 10/10/98\\
  22 & 102 & 10/10/98\\
  22 & 103 & 10/8/98\\
  22 & 104 & 10/7/98\\
  31 & 102 & 11/10/98\\
  31 & 103 & 11/6/98\\
  31 & 104 & 11/12/98\\
  64 & 101 & 9/5/98\\
  64 & 102 & 9/5/98\\
  64 & 103 & 9/5/98\\\hline
\end{tabular}

% Enumerate through all questions.
\begin{itemize}
\item Q1: Find the names of sailors who have reserved boat 103.

  RA1(naive way):\\
  RA1'(Expressing RA1 with cross product):\\
  RA2(push selection, avoid join on large tables):\\
  RA3(push projection):
  \begin{align*}
    &\pi_{sname}(\sigma_{bid=103}(Reserve \bowtie Sailor))\\
    &\pi_{sname}(\sigma_{bid=103}(\sigma_{Reserve.sid=Sailor.sid}(Reserve
    \times Sailor)))\\
    &\pi_{sname}((\sigma_{bid=103}Reserve) \bowtie Sailor)\\
    &\pi_{sname}((\pi_{sid}(\sigma_{bid=103}Reserve)) \bowtie Sailor)\\
  \end{align*}

\item Q2: Find the names of sailors who have reserved a red boat.

  RA1:\\
  RA2(push projection, will generate intermediate relation instances
  with fewer tuples):\\
  \begin{align*}
    &\pi_{sname}((\sigma_{color='red'}Boat) \bowtie Reserve \bowtie
    Sailor)\\
    &\pi_{sname}(\pi_{sid}(\pi_{bid}(\sigma_{color='red'}Boat) \bowtie Reserve) \bowtie
    Sailor)\\
  \end{align*}

\item Q3: Find the colors of boats reserved by Lubber.

  RA: 
  \begin{align*}
    &\pi_{color}(\sigma_{sname='Lubber'}Sailor \bowtie Reserve \bowtie Boat)
  \end{align*}

\item Q4: Find the names of sailors who have reserved at least one
  boat.

  RA:
  \begin{align*}
    &\pi_{sname}(Sailor \bowtie Reserve)
  \end{align*}

\item Q5: Find the names of sailors who have reserved a red or a green
  boat.

  RA:
  \begin{align*}
    &\pi_{sname}((\sigma_{color='red' \lor color='green'}Boat) \bowtie
    Reserve \bowtie Sailor)
  \end{align*}

\item Q6: Find the names of sailors who have reserved a red and a
  green boat.

  RA1:
  \begin{align*}
    &\rho(TmpRel1, (\sigma_{color='red'}Boat) \bowtie Reserve
    \bowtie Sailor)\\
    &\rho(TmpRel2, (\sigma_{color='green'}Boat) \bowtie Reserve
    \bowtie Sailor)\\
    &\pi_{sname}(TmpRel1 \cap TmpRel2)
  \end{align*}

  RA1'(incorrect!!!):
  \begin{align*}
    &\rho(TmpRel1, \pi_{sname}(\sigma_{color='red'}Boat) \bowtie Reserve
    \bowtie Sailor)\\
    &\rho(TmpRel2, \pi_{sname}(\sigma_{color='green'}Boat) \bowtie Reserve
    \bowtie Sailor)\\
    &\pi_{sname}(TmpRel1 \cap TmpRel2)
  \end{align*}

  Note: since \emph{sname} is not a key for the Sailor table, RA1' is
  incorrect. Consider the case when two persons with the same name,
  one reserved only a red boat and another one reserved only a green
  boat, this query will return this name.

  RA2 (more efficient):
  \begin{align*}
    &\rho(TmpRel1, \pi_{sid}((\sigma_{color='red'}Boat) \bowtie
    Reserve))\\
    &\rho(TmpRel1, \pi_{sid}((\sigma_{color='green'}Boat) \bowtie
    Reserve))\\
    &\pi_{sname}((TmpRel1 \cap TmpRel2) \bowtie Sailor)
  \end{align*}

\item Q7: Find the names of sailors who have reserved at least two
  boats.

  RA:
  \begin{align*}
    &\rho(TmpReserve, \pi_{sid, sname, bid}(Sailor \bowtie Reserve))\\
    &\rho(TmpReservePair(1 \rightarrow sid1, 2 \rightarrow sname1, 3
    \rightarrow bid1, 4 \rightarrow sid2, 5 \rightarrow sname2, 6
    \rightarrow bid2),\\
    &TmpReserve \times TmpReserve)\\
    &\pi_{sname}(\sigma_{sid1=sid2 \land bid1 \neq bid2}TmpReservePair)
  \end{align*}

\item Q8: Find the sids of sailors with age over 20 who have not
  reserved a red boat.

  RA:
  \begin{align*}
    \pi_{sid}(\sigma{age>20}Sailor) -
    \pi_{sid}((\sigma_{color='red'}Boat) \bowtie Reserve \bowtie Sailor)
  \end{align*}

\item Q9: Find the names of sailors who have reserved all boats.

  RA:
  \begin{align*}
    &\rho(TmpSid, (\pi_{sid,bid}Reserve) / (\pi_{bid}Boat))\\
    &\pi_{sname}(TmpSid \bowtie Sailor)\\\\
    (\pi_{sid,bid}Reserve) / (\pi_{bid}Boat) &=
    \pi_{sid}Reserve - \pi_{sid}((\pi_{sid}Reserve) \times
    (\pi_{bid}Boat) - \pi_{sid,bid}Reserve)
  \end{align*}

\item Q10: Find the names of sailors who have reserved all boats
  called Interlake.

  RA:
  \begin{align*}
    &\rho(TmpBoat, \pi_{bid}(\sigma_{bname='interlake'}Boat))\\
    &\rho(TmpSid, (\pi_{sid,bid}Reserve) / TmpBoat)\\
    &\pi_{sname}(TmpSid \bowtie Sailor)\\\\
    (\pi_{sid,bid}Reserve) / TmpBoat &=
    \pi_{sid}Reserve - \pi_{sid}((\pi_{sid}Reserve) \times
    TmpBoat - \pi_{sid,bid}Reserve)
  \end{align*}


\end{itemize}
\end{document}
